Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-05-24 props.tex
Quick update of eager integrity to match the others
Made properties explicit about calls, though now returns don't line up right. (In .tex)

@@

    \paragraph{Call States, Returns, and Contours}

@@

      [TODO: be more explicit about what the call map does]
      A state \(m_c\) is a {\it call state} if [call map says it is], and a state \(m_p\) is
      considered to have returned to \(m_c\) if [etc.] From a call state with \(n\) arguments to
      its call, we can construct a contour that should apply inside the call:
      \[Cof(m)(k) =
      \begin{cases}
        (\mathtt{HC},\mathtt{HI}) & \text{if } k \in \mathcal{W}
                                    \text{ and } k \leq m(\mathtt{SP}) - n \\
        (\mathtt{HC},\mathtt{LI}) & \text{if } k \in \mathcal{W}
                                    \text{ and } k \leq m(\mathtt{SP}) \\
        (\mathtt{LC},\mathtt{LI}) & \text{else} \\
      \end{cases}\]

      Above the stack pointer, memory is high integrity in an extension of safe initialization;
      from the perspective of the callee, that memory is not initialized. Below the old stack
      pointer, memory is high integrity and high confidentiality. Registers and the callee's
      frame are low integrity and low confidentiality. These categories inform our integrity
      and confidentiality properties.

@@

      A system enjoys observable integrity if for any initial state \(m_0\), call state \(m_c\),
      policy state \(p_c\), and contour \(C = Cof(m_c)\) such that \(m_0,\mathit{pinit}(m_0)
      \hookrightarrow \dots (m_c,p_c) \dots\):

      \begin{itemize}
        \item If \((m_c,p_c) \hookrightarrow \dots (m_r,p_r) | \mathit{returned}\ m_c\ m_r\):
          \begin{itemize}
            \item Let \(m_r' = \mathit{roll}_I(C,m_c,m_r)\), \((m_r,p_r) \rightsquigarrow O\), and
              \(m_r' \rightsquigarrow O'\)
            \item If \(m_r,p_r \hookrightarrow MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}

@@

      An eager enforcement mechanism implements a stronger property, which we term {\it eager integrity}.
      Eager integrity simplifies observable integrity by requiring that high integrity data of \(m_r\) be
      identical to that of \(m_c\). Formally, a systemctl enjoys eager integrity if for any initial state
      \(m_0\), call state \(m_c\), policy state \(p_c\), and contour \(C = Cof(m_c)\) such that
      \(m_0,\mathit{pinit}(m_0) \hookrightarrow \dots (m_c,p_c) \dots (m_r,p_r) \dots\), where \(\mathit{returned}\ m_c\ m_r\):

@@

      A system enjoys observable confidentiality if for any initial state \(m_0\), call states \(m_c\)
      and \(m_c'\), policy state \(p_c\), and contour \(C = Cof(m_c)\) such that \(m_0,\mathit{pinit}(m_0)
      \hookrightarrow \dots (m_c,p_c) \dots\) and \(m_c \approx_C m_c'\):

      \begin{itemize}
        \item If \((m_c,p_c) \hookrightarrow MP (m_r,p_r) | \mathit{returned}\ m_c\ m_r\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where
              \(m_c' \hookrightarrow M m_r' | \mathit{returned}\ m_c'\ m_r'\)
            \item Let \(m_r'' = \mathit{roll}_C(C,m_c,m_r,m_c',m_r')\),
              \((m_r,p_r) \rightsquigarrow O\), and \(m_r'' \rightsquigarrow O'\)
            \item If \(m_r,p_r \hookrightarrow_P MP \in \top\) then \(O \simeq \mathit{ObsOf}(M) +\!\!\!+ O'\)
            \item Otherwise \(O \lesssim \mathit{ObsOf}(M) +\!\!\!+ O'\)
          \end{itemize}
        \item Else, let \(m_c,p_c \rightsquigarrow O\) and \(m_c' \rightsquigarrow O'\)
          \begin{itemize}
            \item If \(m_c,p_c \hookrightarrow_P MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}

@@

      Once again an eager policy enforces a stronger property that only concerns the behavior of
      the original trace and its variant within each call. A system enjoys {\it eager stack
      confidentiality} if, for any initial state \(m_0\), call states \(m_c\) and \(m_c'\),
      policy state \(p_c\), and contour \(C = Cof(m_c)\) such that \(m_0,\mathit{pinit}(m_0) \hookrightarrow
      \dots (m_c,p_c) \dots\) and \(m_c \approx_C m_c'\):

      \begin{itemize}
        \item If \((m_c,p_c) \hookrightarrow_P MP (m_r,p_r) | \mathit{returned}\ m_c\ m_r\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where
              \(m_c' \hookrightarrow M m_r' | \mathit{returned}\ m_c'\ m_r'\)
            \item \(\mathit{ObsOf}(MP) \simeq \mathit{ObsOf}(M)\)
            \item And for all \(k\), if \(m_c(k) \not = m_r(k)\) or \(m_c'(k) \not = m_r'(k)\),
              \(m_r(k) = m_r'(k)\)
          \end{itemize}
        \item Else, let \(m_c,p_c \rightsquigarrow O\) and \(m_c' \rightsquigarrow O'\)
          \begin{itemize}
            \item If \(m_c,p_c \hookrightarrow_P MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}

>>>>

    \paragraph{Calling Conventions}

      A subroutine call with \(n\) arguments follows the following convention:

      \begin{itemize}
        \item The stack pointer is increased by \(n+1\)
        \item A {\tt Jal} occurs
        \item The return address is stored at \(\mathtt{SP} - (n+1)\)
      \end{itemize}

      The final state of a call sequence state is a {\it call state}. We relate a call sequence \(M\) with
      \(n\) arguments to its final state \(m\) with \(\mathit{isCall}\ M\ m\ n \subset \mathit{trace}\ \mathcal{M}
      \times \mathcal{M} \times \mathbb{N}\).

      A state is considered to have returned after a call if the stack pointer is the same as before the call
      and the program counter is incremented. So:
      \[\mathit{returned}\ m\ m' \triangleq \exists M,n . \mathit{isCall\ M\ m\ n} \land
        m'(\mathtt{SP}) = m(\mathtt{SP}) - (n+1) \land m(\mathtt{PC}) = m'(\mathtt{PC}) + 1\]

@@

    \paragraph{Contours}

@@

      When \(m\) is a call state such that \(\mathit{isCall}\ M\ m\ n\) for some \(M\) and \(n\),
      we can construct a contour based on the size of \(m\)'s stack frame, as follows:
      \[Cof(m)(k) =
      \begin{cases}
        (\mathtt{HC},\mathtt{HI}) & \text{if } k \in \mathcal{W}
                                    \text{ and } k \leq m(\mathtt{SP}) - n \\
        (\mathtt{HC},\mathtt{LI}) & \text{if } k \in \mathcal{W}
                                    \text{ and } k \leq m(\mathtt{SP}) \\
        (\mathtt{LC},\mathtt{LI}) & \text{else} \\
      \end{cases}\]

      Above the stack pointer, memory is high integrity in an extension of safe initialization;
      from the perspective of the callee, that memory is not initialized. At and below the old stack
      pointer, memory is high integrity and high confidentiality -- this includes the return address,
      protecting control flow, as well as the caller's data. Registers and the callee's
      frame are low integrity and low confidentiality. These categories inform our integrity
      and confidentiality properties.

@@

      A system enjoys observable integrity if for any initial state \(m_0\) and call state \(m_c\)
      such that \(m_0,\mathit{pinit}(m_0) \hookrightarrow \dots MP_c (m_c,p_c) \dots\)
      and \(\mathit{isCall}\ MP_c\ m_c\ n\):

      \begin{itemize}
        \item If \((m_c,p_c) \hookrightarrow \dots (m_r,p_r) | \mathit{returned}\ m_c\ m_r\):
          \begin{itemize}
            \item Let \(C = \mathit{Cof(m_c,n)}\)
            \item Let \(m_r' = \mathit{roll}_I(C,m_c,m_r)\), \((m_r,p_r) \rightsquigarrow O\), and
              \(m_r' \rightsquigarrow O'\)
            \item If \(m_r,p_r \hookrightarrow MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}

@@

      An eager enforcement mechanism implements a stronger property, which we term {\it eager integrity}.
      Eager integrity simplifies observable integrity by requiring that high integrity data of \(m_r\) be
      identical to that of \(m_c\). Formally, a system enjoys eager integrity if for any initial state
      \(m_0\) and call state \(m_c\) such that \(m_0,\mathit{pinit}(m_0) \hookrightarrow \dots MP_c (m_c,p_c)
      \dots (m_r,p_r) | \mathit{returned}\ m_c\ m_r\) and \(\mathit{isCall}\ MP_c (m_c,p_c)\):

@@

      A system enjoys observable confidentiality if for any initial state \(m_0\) and call state \(m_c\)
      such that \(m_0,\mathit{pinit}(m_0) \hookrightarrow \dots MP_c (m_c,p_c) \dots\) and
      \(\mathit{isCall}\ MP_c\ m_c\ n\):
      and \(m_c'\),

      \begin{itemize}
        \item Let \(C = \mathit{Cof}(m_c,n)\)
        \item For all \(m_c'\) such that \(m_c \approx_C m_c'\):
        \item If \((m_c,p_c) \hookrightarrow MP (m_r,p_r) | \mathit{returned}\ m_c\ m_r\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where
              \(m_c' \hookrightarrow M m_r' | \mathit{returned}\ m_c'\ m_r'\)
            \item Let \(m_r'' = \mathit{roll}_C(C,m_c,m_r,m_c',m_r')\),
              \((m_r,p_r) \rightsquigarrow O\), and \(m_r'' \rightsquigarrow O'\)
            \item If \(m_r,p_r \hookrightarrow_P MP \in \top\) then \(O \simeq \mathit{ObsOf}(M) +\!\!\!+ O'\)
            \item Otherwise \(O \lesssim \mathit{ObsOf}(M) +\!\!\!+ O'\)
          \end{itemize}
        \item Else, let \(m_c,p_c \rightsquigarrow O\) and \(m_c' \rightsquigarrow O'\)
          \begin{itemize}
            \item If \(m_c,p_c \hookrightarrow_P MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}

@@

      Once again an eager policy enforces a stronger property that only concerns the behavior of
      the original trace and its variant within each call. A system enjoys {\it eager stack
      confidentiality} if, for any initial state \(m_0\) and call state \(m_c\) such that
      \(m_0,\mathit{pinit}(m_0) \hookrightarrow \dots MP_c (m_c,p_c) \dots\) and
      \(\mathit{isCall}\ MP_c\ m_c\ n\):

      \begin{itemize}
        \item Let \(C = \mathit{Cof}(m_c)\)
        \item For all \(m_c'\) such that \(m_c \approx_C m_c'\):
        \item If \((m_c,p_c) \hookrightarrow_P MP (m_r,p_r) | \mathit{returned}\ m_c\ m_r\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where
              \(m_c' \hookrightarrow M m_r' | \mathit{returned}\ m_c'\ m_r'\)
            \item \(\mathit{ObsOf}(MP) \simeq \mathit{ObsOf}(M)\)
            \item And for all \(k\), if \(m_c(k) \not = m_r(k)\) or \(m_c'(k) \not = m_r'(k)\),
              \(m_r(k) = m_r'(k)\)
          \end{itemize}
        \item Else, let \(m_c,p_c \rightsquigarrow O\) and \(m_c' \rightsquigarrow O'\)
          \begin{itemize}
            \item If \(m_c,p_c \hookrightarrow_P MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}
